An Investigation Into The Impact of Transit Improvements on Toronto Traffic Volumes 2010 - 2019

### 2024-04-01 paper/paper.qmd
Added more data to the dataset
Added more rows of data to increase the data size the model is sampled on

---
title: "An Investigation Into The Impact of Transit Improvements on Toronto Traffic Volumes 2010 - 2019"
subtitle: "My subtitle if needed"
author: 
  - Maria Mangru
thanks: "Code and data are available at: https://github.com/MariaMangru/An-Investigation-Into-The-Impact-of-Transit-Improvements-on-Toronto-Traffic-Volumes-2010-2019."
date: today
date-format: long
abstract: "In this study, I have embarked on an analysis of a decade's worth of traffic volume data from critical intersections in Toronto, scrutinizing the effects of public transit developments on urban traffic congestion from 2010 to 2019. [INSERT FINDINGS HERE] The significance of this research lies in its potential to inform and shape urban infrastructure strategies, offering evidence on how transit policies can alleviate traffic pressures in metropolitian areas."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "An Investigation Into The Impact of Transit Improvements on Toronto Traffic Volumes 2010 - 2019"
subtitle: "My subtitle if needed"
author: 
  - Maria Mangru
thanks: "Code and data are available at: https://github.com/MariaMangru/An-Investigation-Into-The-Impact-of-Transit-Improvements-on-Toronto-Traffic-Volumes-2010-2019."
date: today
date-format: long
abstract: "This study investigates the relationship between enhancements in public transit and traffic volumes in metropolitan cities. In particular, this study focuses on the effects caused by the Spadina Subway Extension in Toronto. Data from 2014 - 2019 reveals that both before and after the Subway Extension in 2017, an increase in bus and pedestrian traffic was also related to an increase in car traffic."
format: pdf
number-sections: true
bibliography: references.bib
---
